Safe Transferable Regions

### 2016-07-04 paper/type-inference.tex
added let-region constraint generation rule
Removed elaboration from appendix

\paragraph{Constraint Generation.}
The constraint generation algorithm is a direct adaption of the type checker:
each type checking rule is modified to produce a set of constraints that must hold
for the type checker to succeed.
%
Fig.~\ref{fig:constraint-gen} illustrates this for a couple of rules.
The algorithm proceeds top-down, analyzes an expression $e$ in a context
$\exptycx{\ralloc}{\env}$, and returns a type $\tau$ and a set of constraints $C$
(expressed in the rules as $\exprok {\exptycx{\ralloc}{\env}} {e} {\tau} {C}$ ),
indicating that the expression will have a type $\tau$ provided the constraints $C$ hold.
%
The appendix presents a more detailed algorithm that performs the elaboration and
constraint generation in a single integrated pass.

>>>>

\paragraph{Constraint Generation.}
The constraint generation algorithm is a direct adaption of the type checker:
each type checking rule is modified to produce a set of constraints that must hold
for the type checker to succeed.

Fig.~\ref{fig:constraint-gen} illustrates this for selected language constructs.
These rules use the same context as the expression typing judgment in
Fig.~\ref{fig:fb-staticsem} with symbols $\A$,$\ralloc$, and $\env$
retaining their meaning.
The algorithm proceeds top-down, analyzes an expression $e$ in a context
$\exptycx{\ralloc}{\env}$, and returns a type $\tau$ and a set of constraints $C$
(expressed in the rules as $\exprok {\exptycx{\ralloc}{\env}} {e} {\tau} {C}$ ),
indicating that the expression will have a type $\tau$ provided the constraints $C$ hold.

The rules for generating constraints from a method and
class definition first build a context ($\A$) containing a set ($ \rhoenv$) of region variables denoting
regions that are currently live, a map ($\aenv$) mapping type
variables to their bounds, and a constraint formula ($\phicx$)
capturing constraints over live region variables. We use predicate
variables ($\varphi$ and $\varphi_m$) to capture constraints over
variables in $\rhoenv$ denoting the fact that such constraints are yet
to be inferred.
